---
title: "TFMNs and Cluster coefficients"
author: "Edith Haim"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(ggraph)
library(igraph)
library(cowplot)
library(tidyr)
library(readxl)
library(dplyr)
library(igraph)
```

#### UPDATED CODE
```{r include=FALSE}

FormaMentisNetworks <- function(type = "American", data = "human", category = "Students.low"){
  # Erstelle den Namen des Tabellenblatts
  sheet_name <- paste(type, category, data, sep = "_")

  # Lese die Daten aus der Excel-Datei
  file_path <- "~/PhD Edith Haim/Publications/8. Multiplex PhD Project/0. Network Generating/BFMN Scripts/PhD_FMN_Data.xlsx"
  data_all <- read_excel(file_path, sheet = sheet_name)
  
# Create a data frame for connections
connections <- rbind(
  data_all %>% select(from = cue_word, to = association1),
  data_all %>% select(from = cue_word, to = association2),
  data_all %>% select(from = cue_word, to = association3)
)

# Delete connections that only appear once
connections <- connections %>%
  group_by(from, to) %>%
  filter(n() > 1) %>%
  ungroup()

# Remove missing data
connections <- subset(connections, !is.na(connections$to) & connections$to != "")

# Create a vertices data frame
vertices <- data.frame(name = unique(c(as.character(connections$from), as.character(connections$to))))

# Delete all duplicate connections
connections <- connections %>% distinct(from, to, .keep_all = TRUE)

# Calculate median valence and perform sign test
concept_rating <- rbind(
  data_all %>% select(concept = cue_word, rating),
  data_all %>% select(concept = association1, rating = rating1),
  data_all %>% select(concept = association2, rating = rating2),
  data_all %>% select(concept = association3, rating = rating3)
) %>% filter(concept != "") %>% filter(!is.na(rating))

perform_wilcoxon_test <- function(name) {
  concept_ratings_concept <- subset(concept_rating, concept == name)$rating
  concept_ratings_remaining <- subset(concept_rating, concept != name)$rating
  wilcox_test_result <- wilcox.test(concept_ratings_concept, concept_ratings_remaining, alternative = "two.sided", exact = FALSE)
  return(wilcox_test_result$p.value)
}

properties <- vertices
properties$median_valence <- sapply(properties$name, function(name) {
  median(subset(concept_rating, concept == name)$rating, na.rm = TRUE)
})
properties$median_remaining <- sapply(properties$name, function(name) {
  median(subset(concept_rating, concept != name)$rating, na.rm = TRUE)
})
properties$p_value <- sapply(properties$name, perform_wilcoxon_test)

properties <- properties %>% mutate(valence_category = case_when(
  median_valence > median_remaining & p_value < 0.1 ~ "positive",
  median_valence < median_remaining & p_value < 0.1 ~ "negative",
  TRUE ~ "neutral"
))

# Set node colors based on valence category
properties <- properties %>%
  mutate(node_color = case_when(
    valence_category == "positive" ~ "#3491fa", 
    valence_category == "negative" ~ "#ed382e", 
    valence_category == "neutral" ~ "black",
    TRUE ~ "#bdb7be"  # Default to grey for any other cases
  ))

#create link table
connections2 <- connections
connections2$nodecolor1 <- properties$node_color[match(connections2$from, properties$name)]
connections2$nodecolor2 <- properties$node_color[match(connections2$to, properties$name)]

connections2 <- connections2 %>%
  mutate(link_color = case_when(
    nodecolor1 == "#3491fa" & nodecolor2 == "#3491fa" ~ "#3491fa", 
    nodecolor1 == "#ed382e" & nodecolor2 == "#ed382e" ~ "#ed382e", 
    nodecolor1 == "black" & nodecolor2 == "black" ~ "#bdb7be", 
    (nodecolor1 == "#3491fa" & nodecolor2 == "#ed382e") | 
      (nodecolor1 == "#ed382e" & nodecolor2 == "#3491fa") ~ "purple",
    TRUE ~ "#bdb7be"  # Default to grey for any other cases
  )) 


# Create the graph object (use connections2 so edge attributes exist)
graph <- graph_from_data_frame(connections2, vertices = vertices)

# Attach colors as graph attributes
E(graph)$link_color <- connections2$link_color
V(graph)$node_color <- properties$node_color[match(V(graph)$name, properties$name)]

# Plot the graph
ggraph(graph, layout = 'fr') + 
  geom_edge_link(aes(edge_colour = link_color), width = 1, alpha = 0.8) +
  geom_node_point(aes(color = node_color), size = 5) +
  geom_node_text(aes(label = "", color = node_color), repel = TRUE, size = 5) +
  scale_color_identity() +
  scale_edge_colour_identity() +
  theme_void() +
  theme(legend.position = "none")


}

##############################################

clustering_coefficients <- function(type = "American", data = "human", category = "Students.low"){
  # Erstelle den Namen des Tabellenblatts
  sheet_name <- paste(type, category, data, sep = "_")

  # Lese die Daten aus der Excel-Datei
  file_path <- "~/PhD Edith Haim/Publications/8. Multiplex PhD Project/0. Network Generating/BFMN Scripts/PhD_FMN_Data.xlsx"
  data_all <- read_excel(file_path, sheet = sheet_name)
  

# Create a data frame for connections
connections <- rbind(
  data_all %>% select(from = cue_word, to = association1),
  data_all %>% select(from = cue_word, to = association2),
  data_all %>% select(from = cue_word, to = association3)
)

# Delete connections that only appear once
connections <- connections %>%
  group_by(from, to) %>%
  filter(n() > 1) %>%
  ungroup()

# Remove missing data
connections <- subset(connections, !is.na(connections$to) & connections$to != "")

# Create a vertices data frame
vertices <- data.frame(name = unique(c(as.character(connections$from), as.character(connections$to))))

# Delete all duplicate connections
connections <- connections %>% distinct(from, to, .keep_all = TRUE)

# Calculate median valence and perform sign test
concept_rating <- rbind(
  data_all %>% select(concept = cue_word, rating),
  data_all %>% select(concept = association1, rating = rating1),
  data_all %>% select(concept = association2, rating = rating2),
  data_all %>% select(concept = association3, rating = rating3)
) %>% filter(concept != "") %>% filter(!is.na(rating))

perform_wilcoxon_test <- function(name) {
  concept_ratings_concept <- subset(concept_rating, concept == name)$rating
  concept_ratings_remaining <- subset(concept_rating, concept != name)$rating
  wilcox_test_result <- wilcox.test(concept_ratings_concept, concept_ratings_remaining, alternative = "two.sided", exact = FALSE)
  return(wilcox_test_result$p.value)
}

properties <- vertices
properties$median_valence <- sapply(properties$name, function(name) {
  median(subset(concept_rating, concept == name)$rating, na.rm = TRUE)
})
properties$median_remaining <- sapply(properties$name, function(name) {
  median(subset(concept_rating, concept != name)$rating, na.rm = TRUE)
})
properties$p_value <- sapply(properties$name, perform_wilcoxon_test)

properties <- properties %>% mutate(valence_category = case_when(
  median_valence > median_remaining & p_value < 0.1 ~ "positive",
  median_valence < median_remaining & p_value < 0.1 ~ "negative",
  TRUE ~ "neutral"
))

# Set node colors based on valence category
properties <- properties %>%
  mutate(node_color = case_when(
    valence_category == "positive" ~ "#3491fa", 
    valence_category == "negative" ~ "#ed382e", 
    valence_category == "neutral" ~ "black",
    TRUE ~ "#bdb7be"  # Default to grey for any other cases
  ))

#create link table
connections2 <- connections
connections2$nodecolor1 <- properties$node_color[match(connections2$from, properties$name)]
connections2$nodecolor2 <- properties$node_color[match(connections2$to, properties$name)]

connections2 <- connections2 %>%
  mutate(link_color = case_when(
    nodecolor1 == "#3491fa" & nodecolor2 == "#3491fa" ~ "#3491fa", 
    nodecolor1 == "#ed382e" & nodecolor2 == "#ed382e" ~ "#ed382e", 
    nodecolor1 == "black" & nodecolor2 == "black" ~ "#bdb7be", 
    (nodecolor1 == "#3491fa" & nodecolor2 == "#ed382e") | 
      (nodecolor1 == "#ed382e" & nodecolor2 == "#3491fa") ~ "purple",
    TRUE ~ "#bdb7be"  # Default to grey for any other cases
  )) 

link <- connections2$link_color
link <- lapply(link, function(x) replicate(100,x))
link <- unlist(link, recursive = FALSE)

# Create the graph object
graph <- graph_from_data_frame(connections, vertices = vertices)

deg_seq <- degree(graph)
emperical_clustering_coefficient <- transitivity(graph, type = "average")

clustering_coefficients <- numeric(500)

for (i in 1:500) {
  config_model <- sample_degseq(deg_seq, method = "configuration")

  avg_clustering_coefficient <- transitivity(config_model, type = "average")
  
  clustering_coefficients[i] <- avg_clustering_coefficient
}

# Create a data frame for plotting
clustering_data <- data.frame(clustering_coefficients)

# Plot the histogram and highlight the empirical clustering coefficient
ggplot(clustering_data, aes(x = clustering_coefficients)) +
  geom_histogram(binwidth = 0.01, fill = "lightblue", color = "black") +
  geom_vline(aes(xintercept = emperical_clustering_coefficient), color = "red", linetype = "dashed", linewidth = 1) +
  labs(title = "Distribution of Clustering Coefficients",
       x = "Clustering Coefficient",
       y = "Frequency") +
  theme_minimal() +
  annotate("text", x = emperical_clustering_coefficient, y = max(table(cut(clustering_coefficients, breaks = seq(0, 1, 0.01)))), 
           label = paste("Empirical =", round(emperical_clustering_coefficient, 3)), 
           color = "red", angle = 90, vjust = -0.5, hjust = 1)
}
```


######

## Austrian - Students.high
```{r echo=FALSE}
FormaMentisNetworks(type = "Austrian", data = "human", category = "Students.high")
clustering_coefficients(type = "Austrian", data = "human", category = "Students.high")
```

## Austrian - Students.low

```{r echo=FALSE}
FormaMentisNetworks(type = "Austrian", data = "human", category = "Students.low")
clustering_coefficients(type = "Austrian", data = "human", category = "Students.low")
```

######

## American - Students.high
```{r echo=FALSE}
clustering_coefficients(type = "American", data = "human", category = "Students.high")
FormaMentisNetworks(type = "American", data = "human", category = "Students.high")

```

## American - Students.low
```{r echo=FALSE}
FormaMentisNetworks(type = "American", data = "human", category = "Students.low")
clustering_coefficients(type = "American", data = "human", category = "Students.low")
```

######

## Singapore - Students.high
```{r echo=FALSE}
FormaMentisNetworks(type = "Singapore", data = "human", category = "Students.high")
clustering_coefficients(type = "Singapore", data = "human", category = "Students.high")
```

## Singapore - Students.low
```{r echo=FALSE}
FormaMentisNetworks(type = "Singapore", data = "human", category = "Students.low")
clustering_coefficients(type = "Singapore", data = "human", category = "Students.low")
```

######

## Italian - Students.high
```{r echo=FALSE}
FormaMentisNetworks(type = "Italian", data = "human", category = "Students.high")
clustering_coefficients(type = "Italian", data = "human", category = "Students.high")
```

## Italian - Students.low
```{r echo=FALSE}
FormaMentisNetworks(type = "Italian", data = "human", category = "Students.low")
clustering_coefficients(type = "Italian", data = "human", category = "Students.low")
```

################################

## Austrian - Students.high - AI
```{r echo=FALSE}
FormaMentisNetworks(type = "Austrian", data = "AI", category = "Students.high")
clustering_coefficients(type = "Austrian", data = "AI", category = "Students.high")
```

## Austrian - Students.low - AI

```{r echo=FALSE}
FormaMentisNetworks(type = "Austrian", data = "AI", category = "Students.low")
clustering_coefficients(type = "Austrian", data = "AI", category = "Students.low")
```
######

## American - Students.high - AI
```{r echo=FALSE}
clustering_coefficients(type = "American", data = "AI", category = "Students.high")
FormaMentisNetworks(type = "American", data = "AI", category = "Students.high")

```

## American - Students.low - AI
```{r echo=FALSE}
FormaMentisNetworks(type = "American", data = "AI", category = "Students.low")
clustering_coefficients(type = "American", data = "AI", category = "Students.low")
```

######

## Singapore - Students.high - AI
```{r echo=FALSE}
FormaMentisNetworks(type = "Singapore", data = "AI", category = "Students.high")
clustering_coefficients(type = "Singapore", data = "AI", category = "Students.high")
```

## Singapore - Students.low - AI
```{r echo=FALSE}
FormaMentisNetworks(type = "Singapore", data = "AI", category = "Students.low")
clustering_coefficients(type = "Singapore", data = "AI", category = "Students.low")
```

######

## Italian - Students.high - AI
```{r echo=FALSE}
FormaMentisNetworks(type = "Italian", data = "AI", category = "Students.high")
clustering_coefficients(type = "Italian", data = "AI", category = "Students.high")
```

## Italian - Students.low - AI
```{r echo=FALSE}
FormaMentisNetworks(type = "Italian", data = "AI", category = "Students.low")
clustering_coefficients(type = "Italian", data = "AI", category = "Students.low")
```


######################################

## Network Measures
```{r}
network_measures <- function(type = "American", data = "human", category = "Students.low", save_graph = TRUE){
  # Erstelle den Namen des Tabellenblatts
  sheet_name <- paste(type, category, data, sep = "_")

  # Lese die Daten aus der Excel-Datei
  file_path <- "~/PhD Edith Haim/Publications/8. Multiplex PhD Project/0. Network Generating/BFMN Scripts/PhD_FMN_Data.xlsx"
  data_all <- read_excel(file_path, sheet = sheet_name)

  # Erstelle das Forma Mentis Netzwerk (Struktur bleibt gleich)
  connections <- rbind(
    data_all %>% select(from = cue_word, to = association1),
    data_all %>% select(from = cue_word, to = association2),
    data_all %>% select(from = cue_word, to = association3)
  )

  connections <- connections %>%
    group_by(from, to) %>%
    filter(n() > 1) %>%
    ungroup()

  connections <- subset(connections, !is.na(connections$to) & connections$to != "")
  connections <- connections %>% distinct(from, to, .keep_all = TRUE)

  vertices <- data.frame(name = unique(c(as.character(connections$from), as.character(connections$to))))
  
  # Ungerichtetes Netzwerk erstellen
  graph <- graph_from_data_frame(connections, vertices = vertices, directed = FALSE)

  # Graphen speichern als GraphML für Python
  if (save_graph) {
    file_name <- paste0(type, "_", category, "_", data, ".graphml")
    write_graph(graph, file = file_name, format = "graphml")
    message("Graph saved as: ", file_name)
  }

# Anzahl der Nodes und Edges im gesamten Netzwerk
  num_nodes <- vcount(graph)
  num_edges <- ecount(graph)

  # Größte verbundenen Komponente (LCC) extrahieren
  components <- components(graph, mode = "weak")
  giant_component <- induced_subgraph(graph, which(components$membership == which.max(components$csize)))

  num_nodes_LCC <- vcount(giant_component)
  num_edges_LCC <- ecount(giant_component)
  
  # Netzwerk-Maße berechnen
  ASPL <- mean_distance(graph)   # Average Shortest Path Length
  diameter_value <- diameter(giant_component)  # Diameter
  clustering_coefficient <- transitivity(graph, type = "average")
  
  # Walktrap-Community-Detection (für gerichtete Netzwerke)
  community <- cluster_walktrap(graph)  
  modularity_value <- modularity(community)  

  # Zentralitätsmaße berechnen
  degree_centrality <- mean(degree(graph, mode = "all"))
  pagerank_centrality <- mean(page_rank(graph)$vector)
  
  
  # Ergebnisse in einer Tabelle speichern
  results <- data.frame(
    Measure = c(
      "Nodes in G", "Edges in G", "Nodes in LCC", "Edges in LCC",
      "Diameter", "Average Shortest Path Length", "Clustering", "Modularity",
      "Degree Centrality", "PageRank Centrality"
    ),
    Value = round(c(
      num_nodes, num_edges, num_nodes_LCC, num_edges_LCC,
      diameter_value, ASPL, clustering_coefficient, modularity_value,
      degree_centrality, pagerank_centrality
    ), 4)
  )

  return(results)
}

```


## Calculate Network Measures for Austrian Humans
```{r}
# Funktion ausführen
network_measures(type = "Austrian", data = "human", category = "Teachers")
network_measures(type = "Austrian", data = "human", category = "Students.high")
network_measures(type = "Austrian", data = "human", category = "Students.low")
```

## Calculate Network Measures for American Humans
```{r}
# Funktion ausführen
network_measures(type = "American", data = "human", category = "Students.high")
network_measures(type = "American", data = "human", category = "Students.low")
```

## Calculate Network Measures for Singapore Humans
```{r}
# Funktion ausführen
network_measures(type = "Singapore", data = "human", category = "Students.high")
network_measures(type = "Singapore", data = "human", category = "Students.low")
```

## Calculate Network Measures for Italian Humans
```{r}
# Funktion ausführen
network_measures(type = "Italian", data = "human", category = "Students.high")
network_measures(type = "Italian", data = "human", category = "Students.low")
```

################# AI Data

## Calculate Network Measures for Austrian AI
```{r}
# Funktion ausführen
network_measures(type = "Austrian", data = "AI", category = "Students.high")
network_measures(type = "Austrian", data = "AI", category = "Students.low")
```

## Calculate Network Measures for American AI
```{r}
# Funktion ausführen
#network_measures(type = "American", data = "AI", category = "Teachers")
network_measures(type = "American", data = "AI", category = "Students.high")
network_measures(type = "American", data = "AI", category = "Students.low")
```

## Calculate Network Measures for Singapore AI
```{r}
# Funktion ausführen
network_measures(type = "Singapore", data = "AI", category = "Students.high")
network_measures(type = "Singapore", data = "AI", category = "Students.low")
```

## Calculate Network Measures for Italian AI
```{r}
# Funktion ausführen
network_measures(type = "Italian", data = "AI", category = "Students.high")
network_measures(type = "Italian", data = "AI", category = "Students.low")
```


#################################

## Reshuffling Experiments of undirected BFMNs (for all 4 measures)

```{r}

## Network Measures with Randomized Ensemble
network_measures <- function(type = "American", data = "human", category = "Students.low", n = 500){
  # Load data
  sheet_name <- paste(type, category, data, sep = "_")
  file_path <- "~/PhD Edith Haim/Publications/8. Multiplex PhD Project/0. Network Generating/BFMN Scripts/PhD_FMN_Data.xlsx"
  data_all <- read_excel(file_path, sheet = sheet_name)

  # Create Forma Mentis Network
  connections <- rbind(
    data_all %>% select(from = cue_word, to = association1),
    data_all %>% select(from = cue_word, to = association2),
    data_all %>% select(from = cue_word, to = association3)
  )

  connections <- connections %>%
    group_by(from, to) %>%
    filter(n() > 1) %>%
    ungroup()

  connections <- subset(connections, !is.na(connections$to) & connections$to != "")
  connections <- connections %>% distinct(from, to, .keep_all = TRUE)

  vertices <- data.frame(name = unique(c(as.character(connections$from), as.character(connections$to))))
  
  # Create undirected network
  graph <- graph_from_data_frame(connections, vertices = vertices, directed = FALSE)

  # Compute actual network measures
  ASPL_real <- mean_distance(graph)   
  diameter_real <- diameter(graph)  
  clustering_real <- transitivity(graph, type = "average")

  # Walktrap for community detection
  community <- cluster_walktrap(graph)  
  modularity_real <- modularity(community)  

  # Generate random networks (500 samples)
  deg_seq <- degree(graph)

  ASPL_random <- numeric(n)
  diameter_random <- numeric(n)
  modularity_random <- numeric(n)
  clustering_random <- numeric(n)

  for (i in 1:n) {
    config_graph <- sample_degseq(deg_seq, method = "configuration")
    
    ASPL_random[i] <- mean_distance(config_graph)
    diameter_random[i] <- diameter(config_graph)
    
    # Compute modularity on random graphs
    community_random <- cluster_walktrap(config_graph)
    modularity_random[i] <- modularity(community_random)

    # Compute clustering coefficient on random graphs
    clustering_random[i] <- transitivity(config_graph, type = "average")
  }

  # Compute p-values
  compute_p_value <- function(real_value, random_values) {
    mean_random <- mean(random_values)
    diff_real <- abs(real_value - mean_random)
    count_extreme <- sum(abs(random_values - mean_random) >= diff_real)
    return(count_extreme / n)
  }

  p_value_aspl <- compute_p_value(ASPL_real, ASPL_random)
  p_value_diameter <- compute_p_value(diameter_real, diameter_random)
  p_value_modularity <- compute_p_value(modularity_real, modularity_random)
  p_value_clustering <- compute_p_value(clustering_real, clustering_random)

  # Store results
  results <- data.frame(
    Measure = c("Average Shortest Path Length", "Diameter", "Clustering Coefficient", "Modularity"),
    Empirical = c(ASPL_real, diameter_real, clustering_real, modularity_real),
    Mean_Random = c(mean(ASPL_random), mean(diameter_random), mean(clustering_random), mean(modularity_random)),
    P_Value = c(p_value_aspl, p_value_diameter, p_value_clustering, p_value_modularity)
  )

  return(results)
}

```

```{r}
# Run the function with Austrian Data
network_measures(type = "Austrian", data = "human", category = "Students.low", n = 10000)
network_measures(type = "Austrian", data = "human", category = "Students.high", n = 10000)
```

```{r}
# Run the function with US Data
network_measures(type = "American", data = "human", category = "Students.low", n = 1000)
network_measures(type = "American", data = "human", category = "Students.high", n = 1000)
```
```{r}
# Run the function with SG Data
network_measures(type = "Singapore", data = "human", category = "Students.low", n = 1000)
network_measures(type = "Singapore", data = "human", category = "Students.high", n = 1000)
```

```{r}
# Run the function with IT Data
network_measures(type = "Italian", data = "human", category = "Students.low", n = 1000)
network_measures(type = "Italian", data = "human", category = "Students.high", n = 1000)
```

#### AI Data

```{r}
# Run the function with AT Data
network_measures(type = "Austrian", data = "AI", category = "Students.low", n = 1000)
network_measures(type = "Austrian", data = "AI", category = "Students.high", n = 1000)
```

```{r}
# Run the function with US Data
network_measures(type = "American", data = "AI", category = "Students.low", n = 1000)
network_measures(type = "American", data = "AI", category = "Students.high", n = 1000)
```

```{r}
# Run the function with SG Data
network_measures(type = "Singapore", data = "AI", category = "Students.low", n = 1000)
network_measures(type = "Singapore", data = "AI", category = "Students.high", n = 1000)
```

```{r}
# Run the function with IT Data
network_measures(type = "Italian", data = "AI", category = "Students.low", n = 1000)
network_measures(type = "Italian", data = "AI", category = "Students.high", n = 1000)
```



## Checking why degree centrality is so high
igraph::read_graph("Austrian_Teachers.graphml", format = "graphml")

graph <- read_graph("Austrian_Teachers.graphml", format = "graphml")
hist(degree(graph, mode = "all"), breaks = 20, main = "Degree Distribution")

mean(degree(as.undirected(graph)))

edge_density(graph, loops = FALSE)

